---
title: "QC Example (WICHE)"
output:
  html_document:
    css: ../style.css
    toc: yes
  pdf_document:
    toc: yes
---

```{r warning = FALSE, message = FALSE, echo = FALSE}

source("functions/load.code.R")

```

# Overview

Here is an example of how to use [**datapointsr**](https://github.com/MattjCamp/wicher) 
to do a QC analysis. The content is from WICHE via the [**wicher**](https://github.com/MattjCamp/wicher) package.

I will use the data in wicher to build the two datasets that we want to
compare. BTW this part is going to be a little janky because I have to sort of artifically
create wide datasets for both roles (the Fulfiller and QC Analyst).

First, create the source statistical table:


```{r warning = FALSE, message = FALSE, echo = TRUE}

library(wicher)

d <- wiche_enrollments %>% 
  filter(year %in% 2001:2010,
         grade == "g",
         race == "all",
         location == "us") %>% 
  mutate(variable = sprintf("count_%s", sector),
         value = n) %>% 
  select(year, location, variable, value) %>% 
  wide()

knitr::kable(d)

```

# QC Analysis Examples

## Category & Content Are Off

```{r warning = FALSE, message = FALSE, echo = TRUE}

f <- d
f[3, 4] <- f[3, 4] + sample(1:100, 1)
f[7, 5] <- f[7, 5] + sample(1:1000, 1)
f[8, 2] <- "usa"

q <- d

f <- f %>% long(1:2)
q <- q %>% long(1:2)
dp <- data_points(f, q)
m <- match_data_points(dp)

```

`r show_as_html(m, "Category & Content Are Off")`

## Category Is Missing, But Content Is OK

```{r warning = FALSE, message = FALSE, echo = TRUE}

f <- d
q <- d
f$location <- NULL
f <- f %>% long(1)
q <- q %>% long(1:2)
dp <- data_points(f, q)
m <- match_data_points(dp)
match_data_points <- m

```

`r show_as_html(m, "Category Is Off, But Content Is OK")`


## Perfect Match

```{r warning = FALSE, message = FALSE, echo = TRUE}

f <- d
q <- d
f <- f %>% long(1:2)
q <- q %>% long(1:2)
dp <- data_points(f, q)
m <- match_data_points(dp)

```

`r show_as_html(m, "Perfect Match")`

# Conclusion

`r Sys.getenv("USERNAME")`, `r Sys.time()`

```{r warning = FALSE, message = FALSE, echo = FALSE}

source(sprintf("%s/functions/dispose.code.R",
               here::here()))

```
