---
title: "Sub-Task"
output:
  html_document:
    css: ../style.css
    toc: yes
  pdf_document:
    toc: yes
---

```{r warning = FALSE, message = FALSE, echo = FALSE}

source("functions/load.code.R")

```

This is an example of a QC analysis. We want to see if the
**quakes.csv** file that we have matches the `quakes` dataset
that is built into R.

## Read Fulfiller Data In

```{r warning = FALSE, message = FALSE, echo = TRUE}

f <- 
  read_csv("data-sources/quakes.csv") %>% 
  group_by(stations) %>% 
  summarize(n = length(stations),
            mean_mag = mean(mag))

```

`r knitr::kable(head(f))` 

## Replicate

```{r warning = FALSE, message = FALSE, echo = TRUE}

q <- 
  quakes %>% 
  group_by(stations) %>% 
  summarize(n = length(stations),
            mean_mag = mean(mag))

```

`r knitr::kable(head(q))` 

## QC Analysis

```{r warning = FALSE, message = FALSE, echo = TRUE}

f <- long(f, 1)
q <- long(q, 1)
dp <- data_points(f, q)

```

`r html_matching_report(dp, "QC Match Quakes")`

# NOTES

>**NOTE** `f` is fulfiller dataset and `q` is QC analyst dataset.

>**NOTE** This document was created on `r Sys.time()` by `r Sys.getenv("USERNAME")`.

```{r warning = FALSE, message = FALSE, echo = FALSE}

source(sprintf("%s/functions/dispose.code.R",
               dirname(getwd())))

```
